\documentclass[10pt]{article}
\usepackage{pictex,graphicx,amsmath,amssymb,amssymb,amsbsy,amsfonts,amsthm,verbatim}
\usepackage{graphics}
\usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\setlength{\voffset}{-0,25in}
\setlength{\headsep}{+0,5in}
\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\newcounter{problem}
\newcommand{\problem}{\textbf{\refstepcounter{problem}Problem \theproblem.} }

\def\vu{\mathbf{u}}
\def\vx{\mathbf{x}}
\def\vb{\mathbf{b}}
\def\vv{\mathbf{v}}
\def\vw{\mathbf{w}}
\renewcommand{\implies}{\rightarrow}
\renewcommand{\lor}{\vee}
\renewcommand{\land}{\wedge}
\renewcommand{\iff}{\leffrightarrow}
\newcommand{\xor}{\oplus}
\newcommand{\TRUE}{\mathbf{T}}
\newcommand{\FALSE}{\mathbf{F}}
\newcommand{\universe}{\mathcal{U}}

\begin{document}
\pagestyle{fancyplain}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chead{DISCRETE STRUCTURE (CO1007) --- SOLUTION to Homework 02 --- PREDICATE LOGIC \& PROOF}
%chead{DICRETE STRUCTURE (CC1007) --- Homework 02 --- PREDICATE LOGIC \& PROOF}
\textit{\textbf{\underline{Instruction:}} Type your answers to the following questions provided by LaTeX and submit a zipped file (included .pdf and .tex files) to E-learning by group (only 4-5 members in each group). Only team leader will submit it. One page per problem. Please use the solution template provided.}


\begin{center}
   \begin{tabular}{|c|c|c|c|}
      \hline
      \multicolumn{4}{|c|}{\textbf{GROUP ... ----MEMBER LIST}}\\
      \hline 
      \textbf{No.}  &\qquad\qquad \textbf{Name}\qquad\qquad\qquad & \qquad\textbf{ID}\qquad\qquad & \qquad\textbf{Role}\qquad\qquad \\
      \hline
       1 & Pham Minh Tuan & 1752595 & \\
      \hline
\end{tabular}
\end{center}
\bigbreak
\problem [10pts] Let $F(x,y)$ be the statement "x can fool y", where the domain cosists of all the people to the world. Use the quanlifier to express each of these statements.
\bigbreak 
\textit{Solution:}
\begin{enumerate}

%1

\item   $ \forall x F(x,Fred)$

%2

\item   $ \forall x F(Evelyn,x)$

%3

\item   $ \forall x \exists y F(x,y)$

%4

\item   $ \forall x \forall y \neg(F(y,x))$

%5

\item   $ \forall x \exists y F(y,x)$

%6

\item   $ \forall x \neg(F(x, $Fred$ \land $Jerry$))$

%7

\item   $ \forall x \exists y F(x,y)$

%8

\item   $ \forall x \neg(F(x,$himself$ \lor $herself$)$

%9 
 
\item   $ \exists x F(x,$himself$ \lor $herself$)$
\end{enumerate}

\clearpage
\problem [15pts] Use rules of inference to show that if
    $\forall x (P(x) \lor Q(x)),$
    $\forall x (\neg Q(x) \lor S(x)),$
    $\forall x (R(x) \implies \neg S(x)) and$
    $\forall x \neg P(x)$
    are true, then
    $\exists x \neg R(x)$
    is true. \\
\textit{Solution:}
\begin{enumerate}
%1
\item $\exists x \neg (P(x))$ is true $\therefore P(x)$ is false
%2
\item $\forall x (P(x) \lor Q(x)),$ is true $\therefore Q(x)$ is true $\rightarrow \neg Q(x)$ is false
%3
\item $\forall x (\neg Q(x) \lor S(x)),$ is true $\therefore S(x)$ is true $\rightarrow \neg S(x)$ is false
%4
\item $\forall x (R(x) \implies \neg S(x))$ is true $\therefore R(x)$ is false
%5
\item $\rightarrow \neg R(x)$ is true
\end{enumerate}
 
\clearpage
\problem [10pt] Let L(x,y) be the statement x loves y, where the domain for both x and y consist of all people in the world. Translate the follwing predicate logic into English:
\begin{enumerate}
%1
  \item All people in the world love Jerry
%2
  \item All people in the world love somebody
%3
  \item Somebody loves all people in the world
%4
  \item Lydia doesn't love somebody
%5
  \item All people in the world doesn't love somebody
%6
  \item Y and Z all love only Y
\end{enumerate}   
  
\clearpage
\underline Problem 6 [15pts] Express each of the statements using quantifiers. Then form the negation of the statement so that no negation is to the left of a quanlifier. Next, express the negation in simple English.
\begin{enumerate}
%1
\item All dogs have fleas 
%2
\item There is a horse thet can add
%3
\item Every koala can climb
%4
\item No monkey can speak French
%5
\item There exist a pig that can swim and catch fish

\textit{Solution:}

%1
\item We write this statement as $\forall x (D(x) \implies F(x)$) or $\forall x (\neg D(x) \lor F(x)$). Its negation is $\exists x (D(x) \land \neg F(x)$), and in English it translates into "There is a dog that doesn't have fleas".
%2
\item We write this statement as $\exists x (H(x) \implies A(x)$) or $\exists x (\neg H(x) \lor A(x)$). Its negation is $\forall x (H(x) \land \neg A(x)$), and in English it translates into " All (horses can't add"
%3 
\item We write this statement as $\forall x (K(x) \implies C(x)$) or $\forall x (\neg K(x) \lor C(x)$). Its negation is $\exists x (K(x) \land \neg C(x)$), and in English it translates into " There is a koala that can climb"
%4
\item We write this statement as $\forall x (\neg M(x) \land F(x)$). Its negation is $\exists x (M(x) \lor \neg F(x)$), and in English it translates into " All monkey speak French"
%5
\item We write this statement as $\exists x ( P(x) \implies S(x) \land P(x) \implies C(x)$) or $\exists x (\neg P(x) \lor S(x) \land \neg P(x) \lor C(x)$). Its negation is $\forall x (P(x) \land \neg S(x) and P(x) \land \neg C(x)$), and in English it translates into " All pigs that can't swim and can't catch fish"
\end{enumerate}     
\end{document}
 




































